Hyperparameter Learning \\ for Conditional Mean Embeddings \\ with Rademacher Complexity Bounds

### 2018-05-02 ECML2018/paper/mce_ecml2018.tex
Make references not start on a new page
Test commit for ECML final

\bibliographystyle{apalike}  % Use the "unsrtnat" BibTeX style for formatting the Bibliography
\usepackage[square, authoryear, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography

@@

		% The goal is to motivate the problem here and outline our contribution
		Conditional mean embeddings are nonparametric models that encode conditional expectations in a reproducing kernel Hilbert space, creating a flexible and powerful framework for probabilistic inference. Their performance is greatly dependent on the choice of kernel hyperparameters and regularization parameter. However, current approaches for hyperparameter tuning predominantly rely on cross validation and distance based heuristics. For conditional mean embeddings with categorical targets and arbitrary inputs, we propose a hyperparameter learning framework based on Rademacher complexity bounds to prevent overfitting by balancing data fit against model complexity. The approach only requires batch updates, allowing scalable kernel hyperparameter tuning without kernel approximations. Experiments demonstrate that our framework outperforms competing methods, and can be further extended to incorporate and learn neural network weights improving generalization.

		\keywords{Conditional Mean Embeddings, Kernel Mean Embeddings, Kernel Methods, Mean Embeddings, Hilbert Space Embeddings, Hyperparameter Learning, Rademacher Complexity}
		% % % Original:
		%	We propose learning-theoretic bounds for hyperparameter learning of conditional kernel embeddings for estimating multiclass probabilities. Kernel embeddings are nonparametric methods to represent probability distributions directly through observed data in a reproducing kernel Hilbert space (RKHS). We consider an estimator for multiclass probabilities based on the conditional embedding, with proven stochastic convergence. We then prove that its expected classification error can be bounded with high probability using Rademacher complexity bounds. We use this bound to propose a scalable hyperparameter learning algorithm for conditional embeddings with batch stochastic gradient descent. We apply our learning algorithm to standard UCI datasets, as well as to learn feature representations of a convolutional neural network with improved accuracy, demonstrating the generality of this approach.
	\end{abstract}

@@

	\begin{table*}[t]
		\caption{Test accuracy (\%) on UCI datasets}
		\label{tab:uci_experiments}
		\centering
		\begin{tabular}{lcccccccc}
			Dataset & G\gls{MCE} & G\gls{MCE}-SGD & \gls{CEN}-1 & \gls{CEN}-2 & ERM & CV & MED & Others \\
			\midrule
			\texttt{banknote} & $\mathbf{99.9 \pm 0.2}$ & $98.8 \pm 0.9$ & $99.5 \pm 1.0$ & $99.4 \pm 0.9$ & $\mathbf{99.9 \pm 0.2}$ & $\mathbf{99.9 \pm 0.2}$ & $92.0 \pm 4.3$ & 99.78\textsuperscript{a} \\
			\texttt{ecoli} & $\mathbf{87.5 \pm 4.4}$ & $84.5 \pm 5.0$ & $\mathbf{87.5 \pm 3.2}$ & $86.3 \pm 6.0$ & $72.1 \pm 20.5$ & $73.8 \pm 23.8$ & $42.1 \pm 47.7$ & 81.1\textsuperscript{b} \\
			\texttt{robot} & $\mathbf{96.7 \pm 0.9}$ & $95.5 \pm 0.9$ & $82.3 \pm 7.1$ & $94.5 \pm 0.8$ & $91.0 \pm 3.7$ & $90.9 \pm 3.4$ & $81.1 \pm 6.2$ & 97.59\textsuperscript{c} \\
			\texttt{segment} & $\mathbf{98.4 \pm 0.8}$ & $96.1 \pm 1.5$ & $94.6 \pm 1.6$ & $96.7 \pm 1.1$ & $98.1 \pm 1.1$ & $98.3 \pm 1.3$ & $27.3 \pm 26.4$ & 96.83\textsuperscript{d} \\
			\texttt{wine} & $\mathbf{97.2 \pm 3.7}$ & $93.3 \pm 6.0$ & $96.1 \pm 5.0$ & $97.2 \pm 5.1$ & $93.9 \pm 5.2$ & $93.3 \pm 7.4$ & $93.3 \pm 7.8$ & 100\textsuperscript{e} \\
			\texttt{yeast} & $52.5 \pm 2.1$ & $\mathbf{60.3 \pm 4.4}$ & $55.8 \pm 5.0$ & $59.6 \pm 4.0$ & $45.9 \pm 6.4$ & $58.0 \pm 5.8$ & $31.2 \pm 14.1$ & 55.0\textsuperscript{b} \\
		\end{tabular}
	\end{table*}

@@

@@

%	\begin{thebibliography}{}
	\small{
	\bibliography{kernel_embedding}
	\bibliographystyle{apalike}
	}
%	\end{thebibliography}

>>>>

\bibliographystyle{apalike}  % Use the "unsrtnat" BibTeX style for formatting the Bibliography
\usepackage[square, authoryear, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography
\renewcommand\bibname{References}
\usepackage{etoolbox}
\patchcmd{\bibliography}{\chapter*}{\section*}{}{}
\renewcommand\bibsection{\section*{\refname}}

@@

		% The goal is to motivate the problem here and outline our contribution
		Conditional mean embeddings are nonparametric models that encode conditional expectations in a reproducing kernel Hilbert space, creating a flexible and powerful framework for probabilistic inference. Their performance is greatly dependent on the choice of kernel hyperparameters and regularization parameter. However, current approaches for hyperparameter tuning predominantly rely on cross validation and distance based heuristics. For conditional mean embeddings with categorical targets and arbitrary inputs, we propose a hyperparameter learning framework based on Rademacher complexity bounds to prevent overfitting by balancing data fit against model complexity. The approach only requires batch updates, allowing scalable kernel hyperparameter tuning without kernel approximations. Experiments demonstrate that our framework outperforms competing methods, and can be further extended to incorporate and learn deep neural network weights to improve generalization.

		\keywords{Hyperparameter Learning, Kernel Hyperparameters, Conditional Mean Embeddings, Kernel Mean Embeddings, Kernel Methods, Mean Embeddings, Hilbert Space Embeddings, Reproducing Kernel Hilbert Space, Nonparametric Inference, Rademacher Complexity}
		% % % Original:
		%	We propose learning-theoretic bounds for hyperparameter learning of conditional kernel embeddings for estimating multiclass probabilities. Kernel embeddings are nonparametric methods to represent probability distributions directly through observed data in a reproducing kernel Hilbert space (RKHS). We consider an estimator for multiclass probabilities based on the conditional embedding, with proven stochastic convergence. We then prove that its expected classification error can be bounded with high probability using Rademacher complexity bounds. We use this bound to propose a scalable hyperparameter learning algorithm for conditional embeddings with batch stochastic gradient descent. We apply our learning algorithm to standard UCI datasets, as well as to learn feature representations of a convolutional neural network with improved accuracy, demonstrating the generality of this approach.
	\end{abstract}

@@

@@

%		\begin{table*}[t]
%			\caption{Test accuracy (\%) on UCI datasets}
%			\label{tab:uci_experiments}
%			\centering
%			\begin{tabular}{lcccccccc}	
%				Dataset & G\gls{MCE} & G\gls{MCE}-SGD & \gls{CEN}-1 & \gls{CEN}-2 & ERM & CV & MED & Others \\
%				\midrule
%				\texttt{banknote} & $\mathbf{99.9 \pm 0.2}$ & $98.8 \pm 0.9$ & $99.5 \pm 1.0$ & $99.4 \pm 0.9$ & $\mathbf{99.9 \pm 0.2}$ & $\mathbf{99.9 \pm 0.2}$ & $92.0 \pm 4.3$ & 99.78\textsuperscript{a} \\
%				\texttt{ecoli} & $\mathbf{87.5 \pm 4.4}$ & $84.5 \pm 5.0$ & $\mathbf{87.5 \pm 3.2}$ & $86.3 \pm 6.0$ & $72.1 \pm 20.5$ & $73.8 \pm 23.8$ & $42.1 \pm 47.7$ & 81.1\textsuperscript{b} \\
%				\texttt{robot} & $\mathbf{96.7 \pm 0.9}$ & $95.5 \pm 0.9$ & $82.3 \pm 7.1$ & $94.5 \pm 0.8$ & $91.0 \pm 3.7$ & $90.9 \pm 3.4$ & $81.1 \pm 6.2$ & 97.59\textsuperscript{c} \\
%				\texttt{segment} & $\mathbf{98.4 \pm 0.8}$ & $96.1 \pm 1.5$ & $94.6 \pm 1.6$ & $96.7 \pm 1.1$ & $98.1 \pm 1.1$ & $98.3 \pm 1.3$ & $27.3 \pm 26.4$ & 96.83\textsuperscript{d} \\
%				\texttt{wine} & $\mathbf{97.2 \pm 3.7}$ & $93.3 \pm 6.0$ & $96.1 \pm 5.0$ & $97.2 \pm 5.1$ & $93.9 \pm 5.2$ & $93.3 \pm 7.4$ & $93.3 \pm 7.8$ & 100\textsuperscript{e} \\
%				\texttt{yeast} & $52.5 \pm 2.1$ & $\mathbf{60.3 \pm 4.4}$ & $55.8 \pm 5.0$ & $59.6 \pm 4.0$ & $45.9 \pm 6.4$ & $58.0 \pm 5.8$ & $31.2 \pm 14.1$ & 55.0\textsuperscript{b} \\
%			\end{tabular}
%		\end{table*}

		\begin{table*}[t]
			\caption{Test accuracy (\%) on UCI datasets}
			\label{tab:uci_experiments}
			\centering
			\begin{tabular}{lcccccc}	
				Method         & \texttt{banknote}       & \texttt{ecoli}          & \texttt{robot}          & \texttt{segment}        & \texttt{wine}           & \texttt{yeast}          \\
				\midrule
				G\gls{MCE}     & $\mathbf{99.9 \pm 0.2}$ & $\mathbf{87.5 \pm 4.4}$ & $\mathbf{96.7 \pm 0.9}$ & $\mathbf{98.4 \pm 0.8}$ & $\mathbf{97.2 \pm 3.7}$ & $52.5 \pm 2.1$          \\
				G\gls{MCE}-SGD & $98.8 \pm 0.9$          & $84.5 \pm 5.0$          & $95.5 \pm 0.9$          & $96.1 \pm 1.5$          & $93.3 \pm 6.0$          & $\mathbf{60.3 \pm 4.4}$ \\
				\gls{CEN}-1    & $99.5 \pm 1.0$          & $\mathbf{87.5 \pm 3.2}$ & $82.3 \pm 7.1$          & $94.6 \pm 1.6$          & $96.1 \pm 5.0$          & $55.8 \pm 5.0$          \\
				\gls{CEN}-2    & $99.4 \pm 0.9$          & $86.3 \pm 6.0$          & $94.5 \pm 0.8$          & $96.7 \pm 1.1$          & $97.2 \pm 5.1$          & $59.6 \pm 4.0$          \\
				ERM            & $\mathbf{99.9 \pm 0.2}$ & $72.1 \pm 20.5$         & $91.0 \pm 3.7$          & $98.1 \pm 1.1$          & $93.9 \pm 5.2$          & $45.9 \pm 6.4$          \\
				CV             & $\mathbf{99.9 \pm 0.2}$ & $73.8 \pm 23.8$         & $90.9 \pm 3.4$          & $98.3 \pm 1.3$          & $93.3 \pm 7.4$          & $58.0 \pm 5.8$          \\
				MED            & $92.0 \pm 4.3$          & $42.1 \pm 47.7$         & $81.1 \pm 6.2$          & $27.3 \pm 26.4$         & $93.3 \pm 7.8$          & $31.2 \pm 14.1$         \\
				Others         & 99.78\textsuperscript{a}& 81.1\textsuperscript{b} & 97.59\textsuperscript{c}& 96.83\textsuperscript{d}& 100\textsuperscript{e}  & 55.0\textsuperscript{b}

				%				Dataset           & G\gls{MCE}              & G\gls{MCE}-SGD          & \gls{CEN}-1             & \gls{CEN}-2    & ERM                     & CV                      & MED             & Others \\
				%				\midrule
				%				\texttt{banknote} & $\mathbf{99.9 \pm 0.2}$ & $98.8 \pm 0.9$          & $99.5 \pm 1.0$          & $99.4 \pm 0.9$ & $\mathbf{99.9 \pm 0.2}$ & $\mathbf{99.9 \pm 0.2}$ & $92.0 \pm 4.3$  & 99.78\textsuperscript{a} \\
				%				\texttt{ecoli}    & $\mathbf{87.5 \pm 4.4}$ & $84.5 \pm 5.0$          & $\mathbf{87.5 \pm 3.2}$ & $86.3 \pm 6.0$ & $72.1 \pm 20.5$         & $73.8 \pm 23.8$         & $42.1 \pm 47.7$ & 81.1\textsuperscript{b} \\
				%				\texttt{robot}    & $\mathbf{96.7 \pm 0.9}$ & $95.5 \pm 0.9$          & $82.3 \pm 7.1$          & $94.5 \pm 0.8$ & $91.0 \pm 3.7$          & $90.9 \pm 3.4$          & $81.1 \pm 6.2$  & 97.59\textsuperscript{c} \\
				%				\texttt{segment}  & $\mathbf{98.4 \pm 0.8}$ & $96.1 \pm 1.5$          & $94.6 \pm 1.6$          & $96.7 \pm 1.1$ & $98.1 \pm 1.1$          & $98.3 \pm 1.3$          & $27.3 \pm 26.4$ & 96.83\textsuperscript{d} \\
				%				\texttt{wine}     & $\mathbf{97.2 \pm 3.7}$ & $93.3 \pm 6.0$          & $96.1 \pm 5.0$          & $97.2 \pm 5.1$ & $93.9 \pm 5.2$          & $93.3 \pm 7.4$          & $93.3 \pm 7.8$  & 100\textsuperscript{e} \\
				%				\texttt{yeast}    & $52.5 \pm 2.1$          & $\mathbf{60.3 \pm 4.4}$ & $55.8 \pm 5.0$          & $59.6 \pm 4.0$ & $45.9 \pm 6.4$          & $58.0 \pm 5.8$          & $31.2 \pm 14.1$ & 55.0\textsuperscript{b} \\
			\end{tabular}
		\end{table*}

@@

	\bibliographystyle{apalike}
	\small{
	\bibliography{kernel_embedding}
	}
